Nonlinear methods to quantify Movement Variability in Human-Humanoid Interaction Activities

### 2021-03-18 docs/manuscript/main.tex
polishes fig01 and updates its caption

	State space reconstruction is based on $x(t)=h[s(t)]= h[f^t [s(0)]]$
	where $f^t$ is the true dynamical system, $s(t)$ indicates the state,
    	$s$, at time, $t$,  and $h[ ]$ the measurement function. 
    	The time-delay embedding represented as the $\Phi$, maps the original
    	$d-$dimensional state $s(t)$ into the $m-$dimensional uniform 
	time-delay embedding matrix $\boldsymbol{X}(t)$.
    	The transformation map $\Psi$ then maps $\boldsymbol{X}(t)$ into 
	a new state $y(t)$ of dimensions $n < m$.
    	(A) $M-$dimensional manifold representing the state space 
	(e.g. Lorenz system);
    	(B) Delayed copies of $1-$dimensional $x(t)$ from the Lorenz system;
   	(C) $m-$dimensional reconstructed state space with 
    	\texorpdfstring{$m$}{m} and    \texorpdfstring{$\tau$}{T}, and 
    	(D) $y(t)$ is the $n-$dimensional reconstructed state space.
	The total reconstruction map is represented as $\Xi = \Psi \circ \Phi $
	where $\Phi$ is the delay reconstruction map and 
	$\Psi$ is the coordinate transformation map.
	This figure is adapted from 
   	\cite{Quintana-Duque2012, casdagli1991, uzal2011}.	

@@

	(A) chaotic and (B) random time series.
	(C, D) $E_1 (m)$ values and (E, F) $E_2(m)$ values 
	with variations of $\tau$ values from one to twenty
	for chaotic and random time series.
	(G, H) AMI values where its first minimum value in the curve
	is the minimum time delay embedding ($\tau_0$).

@@

	(A) State space of the Lorenz system with controlling parameters 
	($\rho=28, \sigma=10, \beta=8/3$) where the point, $j$, in trajectory $X()$ which falls into the neighborhood 
	(black circle) of a given point at $i$ is a recurrent point and is 
	represented as a black dot in the recurrence plot at location 
	$(i, j)$ or white otherwise.
	(B) Recurrence plot using the 
	three components of the Lorenz system and the RP with no embeddings 
	and threshold $\epsilon=5$.

@@

	(C) uniformly distributed noise,
	(D) super-positionet harmonic oscillation 
	($sin( \frac{1}{5}*t) * sin( \frac{5}{100}*t) $),
	(E) drift logistic map ($x_{i+1} = 4 x_i (1- x_i) $) corrupted 
	with a linearly increase term ($0.01*i$), and
	(F) disrupted brownian motion  ($x_{i+1} = x_i + 2*rnorm(1) $).
	This figure is adapted from \cite{marwan2015}.

>>>>

		State space reconstruction is based on $x(t)=h[s(t)]= h[f^t [s(0)]]$ where $f^t$ is the true dynamical system, $s(t)$ indicates the state, $s$, at time, $t$,  and $h[ ]$ the measurement function.
		The time-delay embedding represented as the $\Phi$, maps the original $d-$dimensional state $s(t)$ into the $m-$dimensional uniform time-delay embedding matrix $\boldsymbol{X}(t)$.
    	The transformation map $\Psi$ then maps $\boldsymbol{X}(t)$ into a new state $y(t)$ of dimensions $n < m$.
    	(A.1) $M-$dimensional manifold representing the state space (e.g. Lorenz system);
    	(B.1) Delayed copies of $1-$dimensional $x(t)$ from the Lorenz system;
		(C.1) $m-$dimensional reconstructed state space with \texorpdfstring{$m$}{m} and    \texorpdfstring{$\tau$}{T}, and
    	(D.1) $y(t)$ is the $n-$dimensional reconstructed state space.
	The total reconstruction map is represented as $\Xi = \Psi \circ \Phi $where $\Phi$ is the delay reconstruction map and $\Psi$ is the coordinate transformation map.
	A.1 to D.1 figures are adapted from \cite{Quintana-Duque2012, casdagli1991, uzal2011}.

@@

	(A.2) chaotic and (B.2) random time series.
	(C.2, D.2) $E_1 (m)$ values and (E.2, F.2) $E_2(m)$ values with variations of $\tau$ values from one to twenty for chaotic and random time series.
	(G.2, H.2) AMI values where its first minimum value in the curve is the minimum time delay embedding ($\tau_0$).

@@

	(A.3) State space of the Lorenz system with controlling parameters ($\rho=28, \sigma=10, \beta=8/3$) where the point, $j$, in trajectory $X()$ which falls into the neighborhood (black circle) of a given point at $i$ is a recurrent point and is represented as a black dot in the recurrence plot at location $(i, j)$ or white otherwise.
	(B.3) Recurrence plot using the three components of the Lorenz system and the RP with no embeddings and threshold $\epsilon=5$.

@@

	(C.3) uniformly distributed noise,
	(D.3) super-positionet harmonic oscillation ($sin( \frac{1}{5}*t) * sin( \frac{5}{100}*t) $),
	(E.3) drift logistic map ($x_{i+1} = 4 x_i (1- x_i) $) corrupted with a linearly increase term ($0.01*i$), and
	(F.3) disrupted brownian motion  ($x_{i+1} = x_i + 2*rnorm(1) $).
	Figures A.3 to F.3 are adapted from \cite{marwan2015}.
